---
title: "Generic recommender interface"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(Matrix)
library(shiny)
library(flexdashboard)
library(DT)
library(rmarkdown)
library(stopwords)
library(SnowballC)
library(purrr)
library(tidyverse)

library(OutlierIdentifiers)
library(SparseMatrixRecommender)
library(SMRMon)
library(LSAMon)
```

```{r get-data, include=FALSE}

  load( file = "smrGoods.RData" )
  load( file = "lsaGoods.RData" )
  load( file = "dfGoods.RData" )
  
  lsRecommenders <- list( "Goods" = smrGoods)
  lsLSAObjects   <- list( "Goods" = lsaGoods)
  lsData         <- list( "Goods" = dfGoods)
  
  lsRecommenders <- 
    purrr::map( lsRecommenders, function(smr) {
      smr %>% SMRMonApplyTermWeightFunctions( "None", "None", "Cosine" )
    })
```

Parameters {.sidebar}
=======================================================================

```{r}
selectInput( inputId = "recommender", 
             label = "Type:", 
             choices = setNames( names(lsRecommenders), paste( names(lsRecommenders), "recommender" ) ), 
             selected = "Goods")
```


```{r}
smrObj <- 
  reactive({
    lsRecommenders[[ input$recommender ]]
  })

lsaObj <- 
  reactive({
    lsLSAObjects[[ input$recommender ]]
  })

dfData <- 
  reactive({
    lsData[[ input$recommender ]]
  })
```

```{r}
sliderInput( inputId = "numberOfRecs", label = "Number of recommendations:", min = 1, max = 300, value = 10, step = 1 )
```

```{r, echo=F}
uiOutput("dynamic")


output$dynamic <- renderUI({ 
  
  do.call( tagList,
          purrr::map( smrObj() %>% SMRMonTakeTagTypes, function(tt) {
            sliderInput( inputId = paste0( tt, "Weight"), label = paste0( tt, " weight:"), min = 0, max = 1, value = 1, step = 0.01 )
            })
          )

})
```

```{r}
tagTypeWeights <- 
  reactive(
    purrr::map_dbl( smrObj() %>% SMRMonTakeTagTypes, function(tt) { input[[ paste0( tt, "Weight") ]] }) 
  )
```


Main
=======================================================================

Row {data-height=800}
-----------------------------------------------------------------------

### Tags

```{r}
textAreaInput( 
  inputId = "tagsText", 
  label = "Tag text (metadata)", 
  placeholder = "Good:milk, Country:denmark", 
  width = "600px", cols = 300, rows = 8 )

lsTagsProf <- 
  reactive({
    
    if( nchar(input$tagsText) == 0) { 
      NULL 
    } else {
      res <- trimws( strsplit(input$tagsText, split = ",")[[1]] )
      res <- res[ nchar(res) > 0 ]
      res <- res[ res %in% colnames(smrObj()$M) ] 
    }
  })
```

Known tags:

```{r}
renderText(paste(lsTagsProf(), collapse = ", "))
```

### Free text

```{r}
textAreaInput( 
  inputId = "freeText", 
  label = "Free text (description)", 
  placeholder = "Milk unverbalised", 
  width = "600px", cols = 300, rows = 8 )

lsFreeWordsProf <- 
  reactive({
    
    if( nchar(input$freeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTerms( query = input$freeText ) %>% 
        LSAMonTakeValue
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[lsCSums>0]
      
      names(lsProf) <- paste0( "Word:", names(lsProf) )
      lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
      rev(sort(lsProf))
    }
    
  })

lsFreeTopicsProf <- 
  reactive({
    
    if( nchar(input$freeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTopics( query = input$freeText ) %>% 
        LSAMonTakeValue
      
      matRes <- SMRApplyTermWeightFunctions( matRes, "None", "None", "Cosine" )
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[lsCSums>0]
      
      names(lsProf) <- paste0( "Topic:", names(lsProf) )
      lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
      rev(sort(lsProf))
    }
    
  })
```


Extracted words and topics:

```{r}
lsFreeProf <- reactive({ c( lsFreeWordsProf(), lsFreeTopicsProf() ) })
DT::renderDataTable(
  expr = data.frame( Word = names(lsFreeProf()), Score =  lsFreeProf() ),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
)
```

Row
-----------------------------------------------------------------------


### Recommendations with both tags and free text

```{r}
lsProf <- 
  reactive({ 
    c( 
      setNames( rep_len( x = 1, length.out = length(lsTagsProf())), lsTagsProf() ), 
      lsFreeProf() 
    ) 
  })

DT::renderDataTable(
  if( is.null(lsProf()) || length(lsProf()) == 0 ) {
    NULL
  } else {
    smrObj() %>% 
      SMRMonApplyTagTypeWeights( 
        weights = tagTypeWeights(), 
        default = 1 ) %>% 
      SMRMonRecommendByProfile( profile = lsProf(), nrecs = input$numberOfRecs ) %>% 
      SMRMonJoinAcross( dfData() ) %>% 
      SMRMonTakeValue
    },
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```



Profiles
=======================================================================

Row {data-height=800}
-----------------------------------------------------------------------

### Items

```{r}
textAreaInput( inputId = "profileTagsText", label = "Items text (points)", width = "600px", cols = 300, rows = 8 )

lsItemsHist <- 
  reactive({
    
    if( nchar(input$profileTagsText) == 0) { 
      NULL 
    } else {
      res <- trimws( strsplit(input$profileTagsText, split = ",")[[1]] )
      res <- res[ nchar(res) > 0 ]
      res <- res[ res %in% rownames(smrObj()$M) ] 
    }
  })
```

Known items:

```{r}
renderText(paste(lsItemsHist(), collapse = ", "))
```

### Free text

```{r}
textAreaInput( 
  inputId = "profileFreeText", 
  label = "Free text (description)", 
  placeholder = "Milk unverbalised", 
  width = "600px", cols = 300, rows = 8 )

lsProfileFreeWordsProf <- 
  reactive({
    
    if( nchar(input$profileFreeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTerms( query = input$profileFreeText ) %>% 
        LSAMonTakeValue
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[lsCSums>0]
      
      names(lsProf) <- paste0( "Word:", names(lsProf) )
      lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
      rev(sort(lsProf))
    }
    
  })

lsProfileFreeTopicsProf <- 
  reactive({
    
    if( nchar(input$profileFreeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTopics( query = input$profileFreeText ) %>% 
        LSAMonTakeValue
      
      matRes <- SMRApplyTermWeightFunctions( matRes, "None", "None", "Cosine" )
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[lsCSums>0]
      
      names(lsProf) <- paste0( "Topic:", names(lsProf) )
      lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
      rev(sort(lsProf))
    }
    
  })

dfItemsByFreeText <- 
  reactive({
    smrObj() %>% 
      SMRMonApplyTagTypeWeights( 
        weights = tagTypeWeights(),
        default = 1 ) %>% 
      SMRMonRecommendByProfile( profile = lsProfileFreeProf(), nrecs = input$numberOfRecs, normalizeQ = TRUE ) %>% 
      SMRMonTakeValue
  })
    
dfProfileByFreeText <- 
  reactive({
    smrObj() %>% 
      SMRMonProfile( history = setNames(dfItemsByFreeText(), c("Rating", "Index", "Item")), tagTypesQ = TRUE, normalizeQ = TRUE ) %>% 
      SMRMonTakeValue
  })
```


Extracted words and topics:

```{r}
lsProfileFreeProf <- reactive({ c( lsProfileFreeWordsProf(), lsProfileFreeTopicsProf() ) })
DT::renderDataTable(
  expr = data.frame( Word = names(lsProfileFreeProf()), Score =  lsProfileFreeProf() ),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
)
```


Row
-----------------------------------------------------------------------

### Profile of items

```{r}
dfProfileByItemsHist <- 
  reactive({
    smrObj() %>%     
      SMRMonApplyTagTypeWeights( 
        weights = tagTypeWeights(), 
        default = 1 ) %>% 
      SMRMonProfile( history = lsItemsHist(), tagTypesQ = TRUE, normalizeQ = TRUE ) %>% 
      SMRMonTakeValue
  })
```

```{r}
DT::renderDataTable( dfProfileByItemsHist(),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```


### Profile by free text

```{r}
DT::renderDataTable(
  dfProfileByFreeText(),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```


### Profile by both items and free text

```{r}

DT::renderDataTable(
  rbind( dfProfileByItemsHist(), dfProfileByFreeText() ) %>% 
    dplyr::group_by( TagType, Tag) %>% 
    dplyr::summarise( Score = sum(Score), .groups = "drop_last") %>% 
    dplyr::arrange(desc(Score)) %>% 
    dplyr::select( Score, TagType, Tag),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```

Summary
=======================================================================

### Dimensions of the recommender matrix:

```{r}
renderText( dim(smrObj() %>% SMRMonTakeM) )
```

### Tag types and ranges:

```{r}
DT::renderDataTable( smrObj() %>% SMRMonTakeTagTypeRanges )
```


References
=======================================================================

#### In brief

The data of the Goods recommender was generated with the R package
[RandomDataGenerator](https://github.com/antononcube/R-packages/tree/master/RandomDataFrameGenerator), [AAp4].

The recommenders were made with the packages
[`SMRMon-R`](https://github.com/antononcube/R-packages/tree/master/SMRMon-R)
and
[`LSAMon-R`](https://github.com/antononcube/R-packages/tree/master/LSAMon-R),
[AAp1, AAp2, AAp3].


#### Packages 

[AAp1] Anton Antonov,
[Sparse Matrix Recommender framework functions, R-package](https://github.com/antononcube/R-packages/tree/master/SparseMatrixRecommender),
(2019),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).

[AAp2] Anton Antonov,
[Sparse Matrix Recommender Monad, R-package](https://github.com/antononcube/R-packages/tree/master/SMRMon-R),
(2019),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).

[AAp3] Anton Antonov,
[Latent Semantic Analysis Monad, R-package](https://github.com/antononcube/R-packages/tree/master/LSAMon-R),
(2019),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).

[AAp4] Anton Antonov,
[Random Data Frame Generator, R-package](https://github.com/antononcube/R-packages/tree/master/RandomDataFrameGenerator),
(2021),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).
