---
title: "Example obfuscation"
author: "Anton Antonov"
output: html_notebook
---

# Introduction

This document aims at giving basic guidelines for doing data obfuscation with the package 
"DataObfuscation".

# Package load

```{r}
library(DataObfuscation)
```

# The data 

The package comes with a certain transactions data.

```{r}
summary(as.data.frame(unclass(dfMintBubblesTransactions)),maxsum = 20)
```
# Summary of the data 

Here we summarize the data over "Category" and "Account.Name". 
(We do a similar summary over the obfuscated data below.)

```{r}
dfMintBubblesTransactions %>% 
  dplyr::group_by( Category, Account.Name ) %>% 
  dplyr::summarise( GroupTotal = sum(Amount) ) %>% 
  dplyr::arrange(GroupTotal)
```


# Descriptions obfuscation

```{r}
res <-
  ObfuscateDescriptions( descriptions = dfMintBubblesTransactions$Description, 
                         mappedWords = c( "Angela" = "LANDLORD", "AMAZON" = "NETFLIX" ), 
                         preservedWords = c("CANADA", "SAN"), 
                         randomWordsQ = TRUE, randomWordLengthsQ = FALSE )
```

```{r}
grep("Angela", dfMintBubblesTransactions$Description, value = T )
grep("LANDLORD", res, value = T )
```

```{r}
grep("CANADA", dfMintBubblesTransactions$Description, value = T )
grep("CANADA", res, value = T )
```

# Summary of the obfuscated data

Here we summarize the obfuscated data over "Category" and "Account.Name". 
(Compare with the corresponding table above.)

```{r}
dfMintBubblesTransactionsObs <- dfMintBubblesTransactions
dfMintBubblesTransactionsObs$Description <-
  ObfuscateDescriptions( descriptions = dfMintBubblesTransactions$Description, 
                         mappedWords = c( "Angela" = "LANDLORD", "AMAZON" = "NETFLIX" ), 
                         preservedWords = c("CANADA", "SAN"), 
                         randomWordsQ = TRUE, randomWordLengthsQ = FALSE )
dfMintBubblesTransactionsObs$Account.Name <-
  ObfuscateDescriptions( descriptions = dfMintBubblesTransactions$Account.Name, 
                         randomWordsQ = TRUE, randomWordLengthsQ = FALSE )
```

```{r}
dfMintBubblesTransactionsObs %>% 
  dplyr::group_by( Category, Account.Name ) %>% 
  dplyr::summarise( GroupTotal = sum(Amount) ) %>% 
  dplyr::arrange(GroupTotal)
```

