---
title: "Recommender system utilization"
author: Anton Antonov
date: 2020-01-14
output: html_notebook
---

```{r, setup}
library(magrittr)
library(Matrix)
library(SparseMatrixRecommender)
library(SMRMon)
library(LSAMon)
library(DataObfuscation)
```

# Introduction

This notebook shows how to make and use a recommender for investigating the data in this package. 

# Basic workflow

Extend the banking data with an ID column:

```{r}
dfMintBubblesTransactions2 <- cbind( ID = as.character(1:nrow(dfMintBubblesTransactions)), dfMintBubblesTransactions, stringsAsFactors = TRUE )
```

This is how the data looks like:

```{r}
head(dfMintBubblesTransactions2)
```

Create a recommender:

```{r}
smrObj <- 
  SMRMonUnit() %>% 
  SMRMonCreate( data = dfMintBubblesTransactions2, itemColumnName = "ID", addTagTypesToColumnNamesQ = TRUE )
```

Show the recommender tag types:

```{r}
smrObj %>% SMRMonTakeTagTypes()
```

Recommendations by profile:

```{r, rows.print = 20}
smrObj %>% 
  SMRMonRecommendByProfile( profile = c( "Amount:5.75",  "Date:2012-11-12" ), nrecs = 20 ) %>% 
  SMRMonJoinAcross( dfMintBubblesTransactions2, by = "ID" ) %>% 
  SMRMonTakeValue
```

Classify to a "Category" value using a profile:

```{r}
smrObj %>% 
  SMRMonClassifyByProfile( tagType = "Category", profile = c( "Amount:5.75" ) ) %>% 
  SMRMonTakeValue
```

# Elaborations

## Categorization of amounts

Here we categorize the numerical values of the column "Amount":

```{r}
vecCatAmounts <- SMRCategorizeToIntervals( vec = dfMintBubblesTransactions2$Amount, breaks = c( seq(0,100,5), seq(100,300,10), seq(300,1000,100)), intervalNamesQ = TRUE )
vecCatAmounts[1:6]
```

Here we add the categorized amounts as a column to data:

```{r}
dfMintBubblesTransactions2 <- cbind( dfMintBubblesTransactions2, CatAmount = vecCatAmounts, stringsAsFactors = FALSE )
```

Re-create the recommender:

```{r}
smrObj <- 
  SMRMonUnit() %>% 
  SMRMonCreate( data = dfMintBubblesTransactions2, itemColumnName = "ID", addTagTypesToColumnNamesQ = TRUE )
```


Using recommendations by profile retrieve all transactions with amounts between 25 and 30 dollars:

```{r, rows.print = 20}
smrObj %>% 
  SMRMonRecommendByProfile( profile = c( "CatAmount:25≤v<30" ), nrecs = NULL ) %>% 
  SMRMonJoinAcross( dfMintBubblesTransactions2, by = "ID" ) %>% 
  SMRMonTakeValue
```


## Using descriptions words

Using the Latent Semantic Analysis (LSA) software monad `LSAMon` create a description-word matrix and extract topics:

```{r}
lsaObj <- 
  LSAMonUnit( setNames(dfMintBubblesTransactions2$Description, dfMintBubblesTransactions2$ID) ) %>% 
  LSAMonMakeDocumentTermMatrix(stemWordsQ = F, stopWords = NULL) %>% 
  LSAMonApplyTermWeightFunctions( "IDF", "None", "Cosine" ) %>% 
  LSAMonExtractTopics(numberOfTopics = 12, minNumberOfDocumentsPerTerm = 2, method = "NNMF", maxSteps = 20, profilingQ = FALSE ) %>% 
  LSAMonEchoTopicsTable(numberOfTerms = 8, wideFormQ = TRUE )
```

Add the description-term matrix to the recommender:

```{r}
smat <- lsaObj %>% LSAMonTakeWeightedDocumentTermMatrix
colnames(smat) <- paste0("Word:", colnames(smat))
smrObj <- smrObj %>% SMRAnnexSubMatrix( newSubMat = smat, newTagType = "Word" )
```

Show the tag types of the recommender:

```{r}
smrObj %>% SMRMonTakeTagTypes
```

Using recommendations by profile get *purchase* transactions with amounts between 50 and 55 dollars:

```{r, rows.print = 20}
smrObj %>% 
  SMRMonRecommendByProfile( profile = c( "Word:purchase", "CatAmount:50≤v<55" ), nrecs = 6 ) %>% 
  SMRMonJoinAcross( dfMintBubblesTransactions2, by = "ID" ) %>% 
  SMRMonTakeValue
```
