---
title: "Example recommender interface data"
author: Anton Antonov
date: 2021-04-14
output: html_notebook
params:
  randomSeed: 4932
  numberOfRows: 200
  numberOfUsers: 10
  numberOfDays: 90
  numberOfSources: 12
  testRunID: "RandomGoods"
  saveDirectory: "../flexdashboards"
  exportDirectory: "../export"
  saveQ: TRUE
  exportQ: TRUE
---


```{r setup}
library(magrittr)
library(tidyverse)
library(Matrix)
library(SparseMatrixRecommender)
library(SMRMon)
library(LSAMon)
library(OutlierIdentifiers)
library(ParetoPrincipleAdherence)
library(RandomDataFrameGenerator)
```


# Introduction

This notebook creates data for the example recommender interface.


# Parameters

```{r testRunID}
testRunID <- params$testRunID
if( is.null(testRunID) ) {
  testRunID <- paste0( stri_rand_strings(1,4), "-", gsub( " ", "T", as.character(Sys.time()) ) )
  testRunID <- gsub(":", "-", testRunID)
}

predefinedTestsFullFileName <- file.path( params$predefinedTestsDirectoryName, params$predefinedTestsFileName )
```

```{r parameters, rows.print=20}
dfParamsExport <- data.frame( Parameter = names(params), Value = as.character(params) )
rownames(dfParamsExport) <- names(params)
dfParamsExport["testRunID", "Parameter"] <- "testRunID"
dfParamsExport["testRunID", "Value"] <- testRunID
dfParamsExport
```

# Generated data

```{r}
set.seed(params$randomSeed)
lsSources <- RandomWord(200,type = "Common")

MakeRowIDS <- function(n) tolower(paste0( RandomWord(n), "-", round(runif(n = n, min = 0, max = 10 )), "-", RandomString(size = n, lambda = 2)))
lsRowIDs <- MakeRowIDS(params$numberOfRows)
assertthat::assert_that( length(unique(lsRowIDs)) == params$numberOfRows )
```


```{r}
dfGoods <- 
  RandomDataFrame( 
    nrow = params$numberOfRows,
    columnNames = c("ID", "UserID", "Good", "Source", "Country", "TimeStamp"),
    generators = 
      list(
        function(n) tolower(RandomWord(n)),
        gsub( " ", "-", RandomPetName(params$numberOfUsers)),
        c("palms", "washing machines", "cars", "milk", "ham"),
        function(n) purrr::map_chr(1:n, function(x) paste( sample( x = lsSources, size = params$numberOfSources, replace = F), collapse = "; " )),
        c("China", "Germany", "Denmark", "Spain", "USA"),
        function(n) as.character(sort(RandomDate(size = n, min = Sys.time(), max = Sys.time() + params$numberOfDays*24*3600)))
      )
    )
```

```{r}
dfGoods <- 
  dfGoods %>% 
  dplyr::group_by( ID ) %>% 
  dplyr::mutate( ID = paste0( ID, "-", dplyr::row_number() ) ) %>%
  dplyr::ungroup()
```

```{r}
head(dfGoods)
```

```{r}
summary(as.data.frame(unclass(dfGoods), stringsAsFactors = T))
```

```{r}
xtabs(~ UserID + Good, dfGoods )
```


# Transform data

```{r}
dfRandLongForm <- 
  tidyr::pivot_longer( data = dfGoods, cols = setdiff( names(dfGoods), "ID"), names_to = "Variable", values_to = "Value")
dim(dfRandLongForm)
```

```{r}
dfRandLongFormPart <- 
  dfRandLongForm %>% 
  dplyr::filter( Variable == "Source")
dfRandLongFormPart <- 
  purrr::map_df( split(dfRandLongFormPart, 1:nrow(dfRandLongFormPart) ), function(dfX) {
    data.frame( ID = dfX$ID, Variable = dfX$Variable, Value = trimws(strsplit(dfX$Value, ";")[[1]]) )
  })
summary(as.data.frame(unclass(dfRandLongForm), stringsAsFactors = T))
```

```{r}
dfRandLongForm2 <- 
  rbind(
    dfRandLongForm %>% dplyr::filter( Variable != "Source"),
    dfRandLongFormPart
  ) %>% 
  dplyr::mutate( Weight = 1, Value = tolower(Value) )
dim(dfRandLongForm2)
```

# Make recommender

Make invoice-centric, frequencies recommender:

```{r}
smrGoodsFreq <- SMRCreateFromLongForm( data = dfRandLongForm2, itemColumnName = "ID", tagTypeColumnName = "Variable", valueColumnName = "Value", weightColumnName = "Weight", addTagTypesToColumnNamesQ = T )
smrGoodsFreq %>% SMRMonTakeTagTypeRanges
```

```{r}
summary(smrGoodsFreq$M@x)
```

(Heuristically) tuned recommender:

```{r}
smrGoods <- 
  smrGoodsFreq %>% 
  SMRMonApplyTermWeightFunctions("IDF", "None", "Cosine")
```

```{r}
smrGoods %>% SMRMonTakeTagTypeRanges
```

```{r}
summary(smrGoods$M@x)
```

# LSA


```{r}
lsaGoods <- 
  LSAMonUnit( setNames(paste( dfGoods$Source, dfGoods$Country, dfGoods$Good, sep = "; "), dfGoods$ID) ) %>% 
  LSAMonMakeDocumentTermMatrix() %>% 
  LSAMonApplyTermWeightFunctions("IDF", "None", "Cosine") %>% 
  LSAMonExtractTopics( numberOfTopics = 2, minNumberOfDocumentsPerTerm = 1, method = "SVD" ) %>% 
  LSAMonEchoTopicsTable( numberOfTerms = 15, wideFormQ = T)
```

```{r}
dim(lsaGoods %>% LSAMonTakeDocumentTermMatrix)
```

# Extend core goods recommender

```{r}
matWords <- lsaGoods %>% LSAMonTakeWeightedDocumentTermMatrix
matTopics <- lsaGoods %>% LSAMonNormalizeMatrixProduct(normalizeLeftQ = F) %>% LSAMonTakeW
matTopics <- SMRApplyTermWeightFunctions( matTopics, "None", "None", "Cosine" )
```

```{r}
smrGoods <-
  smrGoods %>%
  SMRAnnexSubMatrix( newSubMat = matWords, newTagType = "Word", imposeSameRowNamesQ = T, addTagTypesToColumnNamesQ = T) %>%
  SMRAnnexSubMatrix( newSubMat = matTopics, newTagType = "Topic", imposeSameRowNamesQ = T, addTagTypesToColumnNamesQ = T)
```


# Recommendation examples

## By history

```{r}
focusItem <- rownames(smrGoods$M)[1]
focusItem <- "diametrical-1"
smrGoods %>% 
  SMRMonRecommend(focusItem, nrecs = 10, removeHistoryQ = F, normalizeQ =  F ) %>% 
  SMRMonJoinAcross( data = dfGoods, by = "ID" ) %>% 
  SMRMonTakeValue
```

## By profile

```{r, rows.print = 20}
smrGoods %>% 
  SMRMonRecommendByProfile( profile = c( "Good:milk", "Country:denmark"), nrecs = 10 ) %>% 
  SMRMonTakeValue
```

## Topics

```{r}
query <- "perambulate formic acquired" 
matTerms <- 
  lsaGoods %>% 
  LSAMonRepresentByTerms( query = query, applyTermWeightFunctionsQ = T) %>% 
  LSAMonTakeValue
  
matTerms %>% 
  colSums %>% 
  ( function(x) x[x>0] )
```

```{r}
lsaGoods %>% 
  LSAMonRepresentByTopics( query = query, applyTermWeightFunctionsQ = T, method = "Recommendation") %>% 
  LSAMonTakeValue %>% 
  colSums
```

# Example profiles

```{r, rows.print=20}
focusItem <- rownames(smrGoods$M)[1]
focusItem <- "diametrical-1"
smrGoods %>% 
  SMRMonProfile(focusItem) %>% 
  SMRMonTakeValue
```


# Save

```{r}
if( params$saveQ ) {
  save( smrGoods, file = file.path( params$saveDirectory, "smrGoods.RData") )
  save( lsaGoods, file = file.path( params$saveDirectory, "lsaGoods.RData") )
  save( dfGoods,  file = file.path( params$saveDirectory, "dfGoods.RData") )
}
```

# Export SMR

```{r export-SMR-matrix}
if( params$exportQ ) {
  dfSMRMatrixToExport <- SMRMatricesToLongForm( smr = smrGoods %>% SMRMonSetItemColumnName("Item") )
  dfSMRMatrixToExport <- cbind( TestRunID = testRunID, dfSMRMatrixToExport )
  write.csv( x = dfSMRMatrixToExport, 
             file = file.path( params$exportDirectory, paste0( testRunID, "-dfSMRMatrix.csv")), 
             row.names = FALSE)
}
```

# Export LSA data

```{r export-LSA-data-1}
if( params$exportQ ) {
  
  dfWordToTopicMatrix <- setNames( SMRSparseMatrixToTriplets( lsaGoods %>% LSAMonNormalizeMatrixProduct(normalizeLeftQ = FALSE) %>% LSAMonTakeH ), c("Topic", "Word", "Weight"))
  dfWordToTopicMatrix <- cbind( TestRunID = testRunID, dfWordToTopicMatrix, stringsAsFactors = FALSE )

  write.csv( x = dfWordToTopicMatrix, 
             file = file.path( params$exportDirectory, paste0( testRunID, "-dfLSATopicWordMatrix.csv")), 
             row.names = FALSE)
}
```


```{r export-LSA-data-2}
if( params$exportQ ) {
  
  lsWords <- names(lsaGoods$GlobalWeights)
  lsWeights <- setNames(lsaGoods$GlobalWeights,NULL)
  if ( is.null(lsWords) ) { 
    lsWords <- colnames(lsaGoods %>% LSAMonTakeDocumentTermMatrix) 
  }
  dfGlobalWeights <- data.frame( TestRunID = testRunID, Word = lsWords, Weight = lsWeights, stringsAsFactors = FALSE )
  rownames(dfGlobalWeights) <- NULL

  write.csv( x = dfGlobalWeights, 
             file = file.path( params$exportDirectory, paste0( testRunID, "-dfLSAWordGlobalWeights.csv")), 
             row.names = FALSE)
}
```

Note that no stemming is done; this step is just for completeness.

```{r export-stem-rules}
if( params$exportQ ) {
  
  dfStemRules <- data.frame( Word = names(lsaGoods$GlobalWeights), Stem = names(lsaGoods$GlobalWeights), stringsAsFactors = FALSE)

  write.csv( x = dfStemRules, 
             file = file.path( params$exportDirectory, paste0( testRunID, "-dfStemRules.csv")), 
             row.names = FALSE)
}
```


