---
title: "PRSMon retrieval experiments"
author: Anton Antonov
date: 2020-11-09
output: html_notebook
---

```{r setup}
library(RCurl)
library(jsonlite)
library(magrittr)
library(SMRMon)
library(PRSMon)
```

# Introduction

In order to test the proxy recommender:

1. In a separate R-session run the file ["Example-Web-API-recommender-creation.Rmd"](./Example-Web-API-recommender-creation.Rmd)

2. Run the examples in this file


# Using Proxified SMR

Direct non-PRSMon call to the server (use the correct server address):

```{r}
jsonlite::fromJSON( txt =  RCurl::getURL("http://127.0.0.1:9017/recommend?history=id.12&nrecs=12") )
```

# Verification

Make the proxy object and set the server address:

```{r}
prsObj <- PRSMonUnit() %>% PRSMonSetServerURL( "http://127.0.0.1:9017" )
```

## Recommendations

Recommendations for a list of identifiers:

```{r, rows.print = 20}
prsObj <- 
  prsObj %>% 
  PRSMonRecommend( history = c( "id.12", "id.30"), nrecs = 20, parser = jsonlite::fromJSON ) %>% 
  PRSMonEchoValue
```
## Recommendations by profile

Recommendations by a list of profile tags:

```{r}
prsObj <- 
  prsObj %>% 
  PRSMonRecommendByProfile( profile = c( "male", "1st" ), nrecs = 6, parser = jsonlite::fromJSON ) %>% 
  PRSMonEchoValue
```

## Classify by profile

Classification for a list of profile tags:

```{r}
prsObj <- 
  prsObj %>% 
  PRSMonClassifyByProfile( tagType = "passengerSurvival", profile = c( "female", "1st", "50" ), parser = "json" ) %>% 
  PRSMonEchoValue
```
Show the URL to last query sent to the server:

```{r}
prsObj %>% PRSMonTakeLastQuery
```

Show the last "raw" result from the server:

```{r}
prsObj %>% PRSMonTakeLastResult
```

