---
title: "ROC functions examples"
author: Anton Antonov
date: 2021-02-05
output:
  md_document:
    variant: markdown_github
---


Here we install/load the `ROCFunctions` package from GitHub; 
we also install/load 
[`RandomDataFrameGenerator`](https://github.com/antononcube/R-packages/tree/master/RandomDataFrameGenerator)
which is used in the examples below:

```{r}
#devtools::install_github(repo = "antononcube/R-packages", subdir = "ROCFunctions")
#devtools::install_github(repo = "antononcube/R-packages", subdir = "RandomDataFrameGenerator")
library(ROCFunctions)
library(RandomDataFrameGenerator)
```

Dictionary of Receiver Operating Characteristic (ROC) functions abbreviations and their (descriptive) full names:

```{r}
ROCAcronymsDictionary()
```

Here we compute specified ROCs for a numeric list:

```{r}
ComputeROCFunctions( c("TruePositive" = 15, 
                       "FalsePositive" = 149, 
                       "TrueNegative" = 1523, 
                       "FalseNegative" = 15), c("Precision", "Recall", "PPV") )
```

Here we generate a random data frame with specific column names used to compute ROCs:

```{r}
dfRand <- RandomDataFrame(nrow =  3, columnNames = c("TruePositive", "TrueNegative", "FalsePositive", "FalseNegative"), generators = c( function(x) round(runif(x,0,100))) )
dfRand
```

Verify it is a ROC-data-frame:

```{r}
ROCDataFrameQ(dfRand)
```

Here we compute ROCs over the random data frame above:

```{r}
ROCFunctions::ComputeROCFunctions(dfRand)
```
```{r}
dfRand2 <- 
  RandomDataFrameGenerator::RandomDataFrame( nrow = 200, 
                                             columnNames = c("ActualLBL", "Prob"), 
                                             generators = list( "ActualLBL" = c("0", "1", "9"), "Prob" = function(x) runif(n = x, min = 0, max = 1) )
  )
dfRand2
```

```{r}
ComputeROCTypeCounts(dfRand2, actualColumnName = "ActualLBL", probColumnName = "Prob", thresholds = seq(0,1,0.1))
```

```{r}
ComputeROCTypeCounts(dfRand2, actualColumnName = "ActualLBL", probColumnName = "Prob", thresholds = seq(0,4,0.1))
```


