---
title: "Time series SMR creation"
author: Anton Antonov
date: 2019-04-024
output: html_notebook
---

```{r}
library(SparseMatrixRecommender)
library(SparseMatrixRecommenderInterfacesNoDT)
library(MathematicaVsRData)
library(dplyr)
library(magrittr)
library(shiny)
library(shinydashboard)
```

# Introduction

In this notebook we create a time series search engine based on
[S&P 500](https://en.wikipedia.org/wiki/S&P_500_Index) 
stock daily closing values.

# The data

The data is provided by the (data) package 
[`MathematicaVsRData`](https://github.com/antononcube/R-packages/tree/master/MathematicaVsRData).


```{r}
summary(as.data.frame(unclass(dfSP500)))
```

# Create TS-SMR

Make a sparse matrix:

```{r}
system.time(
  tsMat <- xtabs( Value ~ StockID + Date, dfSP500, sparse = T )
)
```

Normalize matrix:

```{r}
tsDotMat <- SMRApplyTermWeightFunctions( docTermMat = tsMat, globalWeightFunction = "None", localWeightFunction = "None", normalizerFunction = "Cosine")
```

Make the base SMR object:

```{r}
smrSP500 <- SMRCreateFromMatrices( matrices = c(tsDotMat), tagTypes = c("NormalizedTimeSeries"), itemColumnName = "StockID" )
```


Additional derived data for the TS-SMR object (not needed, created automatically if not provided):

```{r, eval=F}
itemIDtoNameRules <- setNames( rownames(tsMat), rownames(tsMat) )
nameToItemIDRules <- setNames( rownames(tsMat), rownames(tsMat) )
tibNameToTIBRules <- setNames( as.POSIXct( colnames(tsMat), format="%Y-%m-%d"), colnames(tsMat) )
```

Make the TS-SMR object:

```{r}
tssmrSP500 <- TSCorrSMRCreate( timeSeriesMatrix = tsMat, smr = smrSP500, smrNRecs = 200 )
```

Here is the S3 class of `tssmr500`:

```{r}
class(tssmrSP500)
```


# Example recommendations 

## Basic

There is specific implementation `Recommendations.TSCorrSMR`.

```{r}
searchID <- "AAPL"
recs <- Recommendations( tssmrSP500, historyItems = searchID, historyRatings = 1, nrecs = 12 )
recs
```

## Lower level functions

```{r}
searchID <- "AAPL"
res <- TSPSRCorrelationNNs( timeSeriesMat = tsMat, smr = smrSP500, itemIDtoNameRules = tssmrSP500$ItemIDtoNameRules, searchRowID = searchID, nrecs = 12, smr.nrecs = 200 )
res
```

# Interface

Make search vectors (not necessary, created automatically if not provided):

```{r, eval=F}
tsSearchVectors <- MakeTimeSeriesSearchVectors( tsMat = tsMat )
length(tsSearchVectors)
```

```{r}
tssmrSP500$TIBNameToTIBRules <- setNames( as.POSIXct(names(tssmrSP500$TIBNameToTIBRules)), names(tssmrSP500$TIBNameToTIBRules) )
```

```{r}
txtNote <- "The S&P 500, or simply the S&P, is a stock market index that measures the stock performance of 500 large companies listed on stock exchanges in the United States. It is one of the most commonly followed equity indices. See https://en.wikipedia.org/wiki/S%26P_500 ."
```

```{r}
shiny::runApp( TSCorrSMRCreateSearchInterface( tsSMR = tssmrSP500, initNNs = 6, initNCols = 2, roundDigits = 4, plotOutputHeight = "800px", dashboardTitle = "S&P 500 search engine", noteText = txtNote, theme = "slate" ) )
```
```{r}
library(magrittr)
mtcars %>% dplyr::filter( mpg > 21) %>% dplyr::select( wt, mpg, am )
```

