---
title: "SMR creation and usage example"
author: Anton Antonov
date: "2019-01-28"
output: html_notebook
---

```{r}
library(SparseMatrixRecommender)
library(Matrix)
library(purrr)
library(magrittr)
library(ggplot2)
```

# Introduction

TBD...

# Installataion

```{r, eval=F}
library(devtools)
devtools::install_github( repo = "antononcube/R-packages", subdir = "SparseMatrixRecommender" )
```


# Data

## Titanic data

```{r}
dfTitanic
```


```{r}
summary(as.data.frame(unclass(dfTitanic)))
```


## Mushroom data

```{r}
dfMushroom
```

```{r}
summary(as.data.frame(unclass(dfMushroom)))
```

# Create SMR classifier

## Split the data

Here we separate the indices of the data.

```{r}
set.seed(2404)
trainingInds <- sample( 1:nrow(dfTitanic), round(0.75*nrow(dfTitanic)))
testInds <- setdiff(1:nrow(dfTitanic), trainingInds)
```

```{r}
trainingData <- dfTitanic[trainingInds,]
testData <- dfTitanic[testInds,]
```

## Class labels

```{r}
labelColumnName <- "passengerSurvival"
```

Here we determine the class label to focus on:

```{r}
focusLabel <- plyr::count( dfTitanic[[labelColumnName]] )
focusLabel <- as.character(focusLabel[which.min(focusLabel$freq),1])
focusLabel
```

## Create SMR directly from data

```{r}
smr <- SMRCreate( trainingData, 
                  tagTypes = setdiff( colnames(trainingData), "id" ), 
                  itemColumnName = "id" )
```


## Create SMR with matrices

```{r}
sMatNames <- colnames(trainingData)[-1]
sMats <- purrr::map( sMatNames, function(x) { xtabs( as.formula( paste0("~ id + ", x) ), trainingData, sparse = TRUE ) } )
names(sMats) <- sMatNames
sMats <- purrr::map( sMats, function(x) { SMRApplyTermWeightFunctions( x, "IDF", "None", "None" ) } )
smr2 <- SMRCreateFromMatrices( matrices = sMats, itemColumnName = "id" )
```

### Same matrices check

```{r}
smat1 <- SMRSubMatrix( smr, "passengerAge" )
smat2 <- SMRMakeRowStochastic( SMRSubMatrix( smr2, "passengerAge" ) )
norm(as.matrix(smat1 - smat2))
```


## Recommendations by profile

```{r}
dfTitanic %>% 
  dplyr::filter( passengerSex == "female" & passengerAge == 30 )
```

```{r}
prof <- SMRProfileDF( smr, itemHistory = data.frame( Rating = c(1,1,1), Item = c("id.1", "id.14", "id.33"), stringsAsFactors = F ) )
prof
```

```{r}
recs <- SMRRecommendationsByProfileDF( smr = smr, profile = prof[, 1:2], nrecs = 12 )
recs %>% dplyr::inner_join( dfTitanic, by = "id" )
```

```{r, rows.print = 20}
recs2 <- SMRRecommendationsByProfileDF( smr = smr2, profile = prof[, 1:2], nrecs = NULL )
recs2 %>% dplyr::inner_join( dfTitanic, by = "id" )
```

# Classify

## Using the direct-SMR classifier

```{r}
clRes <- predict( smr, 
                  testData[, grep( labelColumnName, colnames(testData), invert = T )], 
                  nTopNNs = 20, type = "decision", tagType = labelColumnName )
```

```{r}
xtabs( ~ Actual + Predicted, data.frame( Actual = testData[[labelColumnName]], Predicted = clRes, stringsAsFactors = F))
```

## Using the TF-IDF SMR classifier

```{r}
clRes2 <- predict( smr2, 
                   testData[, grep( labelColumnName, colnames(testData), invert = T )], 
                   nTopNNs = 20, type = "decision", tagType = labelColumnName )
```

```{r}
xtabs( ~ Actual + Predicted, data.frame( Actual = testData[[labelColumnName]], Predicted = clRes2, stringsAsFactors = F))
```

## Using matrices

```{r}
smr$M01[1:5,(ncol(smr$M01)-1):ncol(smr$M01)]
```

```{r}
predict( smr, 
         smr$M01[1:15,], 
         nTopNNs = 20, type = "scores", tagType = labelColumnName )
```

# Distances within classes

```{r}
smr$TagTypes
```

```{r}
dfDists <- SMRDistances( smr, tagType = NULL, method = "euclidean" )
dfDists
```

```{r}
ggplot(dfDists) +
  geom_histogram( aes(x = Distance), bins = 30 ) +
  facet_wrap( ~ TagType + Tag, scales = "free_y" )
```


