---
title: "SMR export and import examples"
author: Anton Antonov
date: 2020-11-03
output: html_notebook
---

```{r setup}
library(SparseMatrixRecommender)
library(Matrix)
```

# Introduction

This notebook has examples of SMR objects imports and exports.

# Make a recommender

Create recommender and apply LSI functions to its matrix:

```{r}
smrTitanic <- SMRCreate(dfTitanic)
smrTitanic$M01 <- SMRApplyTermWeightFunctions( smrTitanic$M01, "IDF", "None", "None" )
```

# Export recommender

Export recommender to specified directory using a specified recommender file names infix:

```{r}
SMRExportToDirectory( smr = smrTitanic, directoryPath = "../SMR-export", dataNamePrefix = "Titanic", dataNameInfix = "DFDWKL", csvTripletsQ = TRUE, digits = 4 )
```


# Import recommender

Import recommender from specified directory and recommender file names infix:

```{r}
smrTitanic2 <- SMRImportFromDirectory( directoryPath = "../SMR-export", dataNamePrefix = "Titanic", dataNameInfix = "DFDWKL" )
```

# Verify

Same tag types:

```{r}
mean(smrTitanic$TagTypes == smrTitanic$TagTypes)
```

Same row names:

```{r}
mean(rownames(smrTitanic$M) == rownames(smrTitanic2$M))
```

Same column names:

```{r}
mean(colnames(smrTitanic$M) == colnames(smrTitanic2$M))
```

Same 0-1 matrices:

```{r}
norm(smrTitanic$M01 - smrTitanic2$M01)
```

Same recommendation matrices after application of LSI functions:

```{r}
smrTitanic2$M <- SMRApplyTermWeightFunctions( smrTitanic2$M, "IDF", "None", "Cosine")
norm(smrTitanic$M - smrTitanic2$M)
```

