---
title: "Time series SMR creation"
author: Anton Antonov
date: 2019-04-024
output: html_notebook
---

```{r}
library(SparseMatrixRecommender)
library(MathematicaVsRData)
library(shinydashboard)
```

# Introduction

In this notebook we create a time series search engine based on
[S&P 500](https://en.wikipedia.org/wiki/S&P_500_Index) 
stock daily closing values.

# The data

The data is provided by the (data) package 
[`MathematicaVsRData`](https://github.com/antononcube/R-packages/tree/master/MathematicaVsRData).


```{r}
summary(as.data.frame(unclass(dfSP500)))
```

# Create TS-SMR

Make a sparse matrix:

```{r}
system.time(
  tsMat <- xtabs( Value ~ StockID + Date, dfSP500, sparse = T )
)
```

Make the base SMR object:

```{r}
smrSP500 <- SMRCreateFromMatrices( matrices = c(tsMat), tagTypes = c("TimeSeries"), itemColumnName = "StockID" )
```


Additional derived data for the TS-SMR object (not needed, created automatically if not provided):

```{r, eval=F}
itemIDtoNameRules <- setNames( rownames(tsMat), rownames(tsMat) )
nameToItemIDRules <- setNames( rownames(tsMat), rownames(tsMat) )
tibNameToTIBRules <- setNames( as.POSIXct( colnames(tsMat), format="%Y-%m-%d"), colnames(tsMat) )
```

Make the TS-SMR object:

```{r}
tssmrSP500 <- TSCorrSMRCreate( timeSeriesMatrix = tsMat, smr = smrSP500, smrNRecs = 200 )
```

Here is the S3 class of `tssmr500`:

```{r}
class(tssmrSP500)
```


# Example recommendations 

## Basic

There is specific implementation `Recommendations.TSCorrSMR`.

```{r}
searchID <- "AAPL"
recs <- Recommendations( tssmrSP500, historyItems = searchID, historyRatings = 1, nrecs = 12 )
recs
```

## Lower level functions

```{r}
searchID <- "AAPL"
res <- TSPSRCorrelationNNs( timeSeriesMat = tsMat, smr = smrSP500, itemIDtoNameRules = tssmrSP500$ItemIDtoNameRules, searchRowID = searchID, nrecs = 12, smr.nrecs = 200 )
res
```

# Interface

Make search vectors (not necessary, created automatically):

```{r, eval=F}
tsSearchVectors <- MakeTimeSeriesSearchVectors( tsMat = tsMat )
length(tsSearchVectors)
```


```{r}
shiny::runApp( TSCorrSMRCreateSearchInterface( tsSMR = tssmrSP500 ) )
```

