---
title: "State monad code generation example"
author: Anton Antonov
date: 2019-03-02
output: html_notebook
---

# Introduction

In this notebook we demonstrate 
[State monad](https://en.wikipedia.org/wiki/Monad_(functional_programming)#State_monads) 
code generation and a pipeline usage.

For more details on monad code generation see [1, 1a].


## Installation

Install the code generation package with following command.

```{r, eval=FALSE}
devtools::install_github( "antononcube/R-packages", subdir = "StateMonadCodeGenerator")
```

## Package load

```{r}
library(StateMonadCodeGenerator)
```

# Generate State monad code

```{r}
rCodeFileName <- "~/R-packages/StateMonadCodeGenerator/generated-code/StMon.R"
genCode <- 
  GenerateStateMonadCode( outputFile = rCodeFileName, 
                          monadName = "StMon", 
                          memberNames = c("Data" = "numeric", "RegressionFunctions" = "list", "Outliers" = "list" ), 
                          monadObjectArgumentName = "qrObj"  )
```

## Additional code changes

Additional code changes might be required after the generation.
For example, changing the code to use the correct class functions for the monad members
in the setter and taker functions.

## Parsing the code

We load the code by parsing the generated code lines.

```{r}
eval(parse( text = genCode ))
```

Alternatively, if we specified a valid file name to `GenerateStateMonadCode`
we can use that file.

```{r}
source(rCodeFileName)
```

# Experiments with the generated code

```{r}
StMonUnit() %>% 
  StMonSetData( runif(n = 10, min = 10, max = 30) ) %>% 
  StMonTakeData
```


# References

[1] Anton Antonov, 
["Monad code generation and extension"](https://mathematicaforprediction.wordpress.com/2017/06/23/monad-code-generation-and-extension/),
(2017),
[MathematicaForPrediction at WordPress](https://mathematicaforprediction.wordpress.com).

[1a] Anton Antonov, 
["Monad code generation and extension"](https://github.com/antononcube/MathematicaForPrediction/blob/master/MarkdownDocuments/Monad-code-generation-and-extension.md),
(2017),
[MathematicaForPrediction at GitHub](https://github.com/antononcube/MathematicaForPrediction).
